---
title: "Final report"
author: "Petr Perina, add your name here"
date: "September 26, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Final report

Formatting etc. TBD

First filter the data

```{r}
load('data_short.Rdata')
library(dplyr)

# Filter data based on agreed conditions
data_filt <- filter(data_short, data_short$number_of_reviews >= 3 & data_short$property_type == "Apartment" & data_short$room_type == "Private room")

# Drop all rows with NAs
data_filt <- na.omit(data_filt)

nrow(data_filt)
# We still have 7259 rows which is pretty decent
```
Strategy: run a regression with all reasonable variables, remove the one with the highest P-value, re-run until we get a satisfactory model.

1) Remove filter variables, zipcode, zip_first and turn relevant variables into factors. Use only distance and not lat & long. Use only count of amenities.

The result is the first regression.
```{r}
# double check price_pp definition
data_filt$cancellation_policy <- factor(data_filt$cancellation_policy)
fit <- lm(data_filt$price_pp ~ data_filt$accommodates + data_filt$bathrooms + data_filt$bedrooms + data_filt$beds + data_filt$guests_included + data_filt$minimum_nights + data_filt$number_of_reviews + data_filt$review_scores_rating + data_filt$review_scores_accuracy + data_filt$review_scores_cleanliness + data_filt$review_scores_checkin + data_filt$review_scores_communication + data_filt$review_scores_location + data_filt$review_scores_value + data_filt$instant_bookable + data_filt$cancellation_policy + data_filt$distance + data_filt$amenities_count)
summary(fit)
```
Now remove insignificant variables one by one until we have a satisfactory model. R^2 of the first model in which all variables are significant at the 5% level is only 0.28
```{r}
fit2 <- lm(data_filt$price_pp ~ data_filt$accommodates + data_filt$bathrooms + data_filt$bedrooms + data_filt$guests_included + data_filt$review_scores_rating + data_filt$review_scores_accuracy + data_filt$review_scores_cleanliness + data_filt$review_scores_location + data_filt$review_scores_value + data_filt$distance + data_filt$amenities_count)
summary(fit2)
```

If we want to have all variables significant at 1% level this is what we get
```{r}
fit3 <- lm(data_filt$price_pp ~ data_filt$accommodates + data_filt$bathrooms + data_filt$bedrooms + data_filt$guests_included + data_filt$review_scores_rating + data_filt$review_scores_cleanliness + data_filt$review_scores_location + data_filt$review_scores_value + data_filt$distance + data_filt$amenities_count)
summary(fit3)
```

